%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research}

%-------------------------------------------------------------------------------
% INTERESTS
%-------------------------------------------------------------------------------
\cvsubsection{Interests}

\begin{cvparagraph}
  Health AI~~~~·~~~~Digital Medicine~~~~·~~~~Precision Medicine~~~~·~~~~Predictive
  Modeling~~~~·~~~~Bioinformatics~~~~·~~~~Patient Reported Outcome Measures (PROMs)
\end{cvparagraph}

%-------------------------------------------------------------------------------
% EXPERIENCES
%-------------------------------------------------------------------------------
\cvsubsection{Experiences}

\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Duke University School of Medicine} % Organization
  {Department of Orthopaedic Surgery — Li Lab} % Job title
  {Durham, NC} % Location
  {August 2024 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Investigated how pharmacologic and non-pharmacologic modalities affect peripheral nerve regeneration following injury.}
    \item {Developed large language model (LLM) based methods to automate
      literature reviews.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {University of Massachusetts Chan Medical School} % Organization
  {Program in Digital Medicine — Lin Lab} % Job title
  {Worcester, MA} % Location
  {June 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed deep neural network–based methods to estimate age from
        electrocardiograms (ECGs) and machine learning models to predict the
      risk of future disease.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Brown University} % Organization
  {Center of Computational Molecular Biology — Bailey Lab} % Job title
  {Providence, RI} % Location
  {January 2020 - August 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked as an undergraduate lab member and then as a bioinformatician
      following graduation.}
    \item {Developer for coiaf, a package to estimate the number of malarial
      strains a patient is infected with}
    \item {Developer for MIPTools, a suite of computational tools for molecular
      inversion probe design, data processing, and analysis.}
    \item {Developer for miplicorn, a unified framework for molecular inversion
      probe (MIP) and amplicon-targeted sequencing analysis following micro haplotyping or variant calling.}
    \end{cvitems}
  }

  \cventry
  {} % Organization
  {Center for Evidence-Based Synthesis} % Job title
  {} % Location
  {May 2018 - January 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked with Prof. Schmid to create a package to analyze
      single-patient (N-of-1) clinical trials.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Massachusetts General Hospital} % Organization
  {Department of Orthopaedic Surgery} % Job title
  {Boston, MA} % Location
  {May 2019 - September 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked as a research intern in the trauma department, shadowing
      doctors and conducting research primarily with Dr. Heng.}
    \item {Focused on examining associations between mental health scores
        and physical function scores of patients who had recently undergone
      total knee or hip replacements.}
    \end{cvitems}
  }

  \cventry
  {} % Organization
  {Cardiovascular Research Center} % Job title
  {} % Location
  {May 2019 - December 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked under the direction of Dr. Das, Dr. Varrias, and Dr.
        Rodosthenous as a recipient of an American Heart Association summer
      fellowship.}
    \item {Examined associations between micro RNAs, long non-coding RNAs, and
      heart failure using computational techniques.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Massachusetts Institute of Technology} % Organization
  {Operations Research Center} % Job title
  {Cambridge, MA} % Location
  {June 2016 - September 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked with Dr. Bertsimas and Dr. Dunn on regression and
        classification problems using an approach that derives optimal decision
      trees by solving an integer optimization problem.}
    \end{cvitems}
  }

  \cventry
  {} % Organization
  {Operations Research Center} % Job title
  {} % Location
  {June 2015 - September 2015} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked with Dr. Bertsimas on a regression problem with an
      application to ophthalmology.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
