%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\vspace{-2mm}
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Duke University School of Medicine} % Organization
  {Department of Orthopaedic Surgery — Li Lab} % Job title
  {Durham, NC} % Location
  {August 2024 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Investigated how pharmacologic and non-pharmacologic modalities
      affect peripheral nerve regeneration following injury.}
    \item {Developed large language model (LLM) based methods to automate
      literature reviews.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {University of Massachusetts Chan Medical School} % Organization
  {Program in Digital Medicine — Lin Lab} % Job title
  {Worcester, MA} % Location
  {June 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed deep neural network–based methods to estimate age from
        electrocardiograms (ECGs) and machine learning models to predict the
      risk of future disease.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Brown University} % Organization
  {Center of Computational Molecular Biology — Bailey Lab} % Job title
  {Providence, RI} % Location
  {January 2020 - August 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked as an undergraduate lab member and then as a bioinformatician
      following graduation.}
    \item {Developer for coiaf, a package to estimate the number of malarial
      strains a patient is infected with}
    \item {Developer for MIPTools, a suite of computational tools for molecular
      inversion probe design, data processing, and analysis.}
    \item {Developer for miplicorn, a unified framework for molecular inversion
        probe (MIP) and amplicon-targeted sequencing analysis following micro
      haplotyping or variant calling.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Massachusetts General Hospital} % Organization
  {Department of Orthopaedic Surgery} % Job title
  {Boston, MA} % Location
  {May 2019 - September 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked as a research intern in the trauma department, shadowing
      doctors and conducting research primarily with Dr. Heng.}
    \item {Focused on examining associations between mental health scores and
        physical function scores of patients who had recently undergone total
      knee or hip replacements.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
